A meta-analysis of mental rotation ability in the first years of life

### 2022-04-22 code/analysis.Rmd
Align structure of code blocks with the manuscript

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  fig.height = 10,
  fig.width = 7.5,
  out.width = "100%"
)

@@

Effect sizes of individual experiments:

```{r, compute_effects, echo=TRUE}
# Add columns to the table of included experiments
included %>%
  mutate(

@@

    # Convert gender to a categorical variable
    gender = case_when(
      female_percent == 1.0 ~ "female",
      female_percent == 0.0 ~ "male",
      TRUE ~ "mixed"
    ) %>% factor(levels = c("mixed", "female", "male")),

    # Convert mean sample age from days to months and center
    age_months = age_mean / 30.417,
    age = age_months - mean(age_months, na.rm = TRUE),

@@

# Compute standard error of Cohen's d based on assumed correlation
# See Hedges' formula on p. 253 in http://dx.doi.org/10.20982/tqmp.14.4.p242
# This will need a sensitivity analysis regarding the values of `r_assumed`
r_assumed <- 0.5
dat_all %>%
  mutate(
    ni = sample_size,
    vi = (dfi / (dfi - 2)) * ((2 * (1 - r_assumed)) / ni) *
      (1 + gi^2 * (ni / (2 * (1 - r_assumed)))) - (gi^2 / ji^2),
    sei = sqrt(vi)
  ) %>%
  filter(!is.na(gi)) %>%
  select(
    article,
    group,
    experiment,
    gender_split,
    gi,
    ni,
    vi,
    sei,
    gender,
    age
  ) -> dat_all_r

@@

# We go ahead with the last solution as to use the maximum amount of information
# while not biasing the gender results
dat <- dat_both_mixed
```

Actual meta-analysis:

```{r, compute_meta, echo=TRUE}
# Three-level model
res_ml <- rma.mv(
  gi, vi,
  random = ~ 1 | article / experiment,
  data = dat,
  slab = experiment
)
print(res_ml)
# forest(res_ml)

# # Profile likelihodd plots for checking that REML has converged
# profile(res_ml)

# Apply sliding difference contrast coding for the gender categories
# This means that the Intercept will be the grand mean (i.e., the average across
# studies) whereas the betas will test female vs. mixed and male vs. female
(contrasts(dat$gender) <- MASS::contr.sdif(3))

```{r, brms, echo=TRUE}
# Specify priors
prior_c <- c(
  set_prior("normal(0, 1)", class = "Intercept"),
  set_prior("cauchy(0, 0.3)", class = "sd")
)

@@

```{r, prior_sens, eval=FALSE}
# Prior sensitivity analysis
list(
  "interept_uninformative" = c(
    set_prior("uniform(-3, 3)", class = "Intercept"),
    set_prior("cauchy(0, 0.3)", class = "sd")
  ),
  "interept_informative" = c(
    set_prior("normal(0, 0.2)", class = "Intercept"),
    set_prior("cauchy(0, 0.3)", class = "sd")
  ),
  "sd_uninformative" = c(
    set_prior("normal(0, 1)", class = "Intercept"),
    set_prior("uniform(0, 10)", class = "sd", ub = 10)
  ),
  "sd_informative" = c(
    set_prior("normal(0, 1)", class = "Intercept"),
    set_prior("student_t(10, 0, 0.2)", class = "sd")
  )
) %>%
  map(function(prior_sens) update(res_brm, prior = prior_sens)) -> res_sens
map(res_sens, summary)
```

@@

>>>>

# Global chunk options
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  fig.height = 10,
  fig.width = 7.5,
  out.width = "100%"
)

@@

## Mental rotation ability

```{r, prepare_effect_sizes}
# Add columns to the table of included experiments
included %>%
  mutate(

@@

@@

# Compute standard error of Cohen's d based on assumed correlation
# See Hedges' formula on p. 253 in http://dx.doi.org/10.20982/tqmp.14.4.p242
# This will need a sensitivity analysis regarding the values of `r_assumed`
r_assumed <- 0.5
dat_all %>%
  mutate(
    ni = sample_size,
    vi = (dfi / (dfi - 2)) * ((2 * (1 - r_assumed)) / ni) *
      (1 + gi^2 * (ni / (2 * (1 - r_assumed)))) - (gi^2 / ji^2),
    sei = sqrt(vi)
  ) %>%
  filter(!is.na(gi)) %>%
  select(
    article,
    group,
    experiment,
    gender_split,
    gi,
    ni,
    vi,
    sei,
    female_percent,
    age_mean
  ) -> dat_all_r

@@

# We go ahead with the last solution as to use the maximum amount of information
# while not biasing the gender results
dat_select <- dat_both_mixed

# Recode predictor variables for meta-regression and plotting
dat_select %>%
  mutate(

  # Gender as a categorical variable
  gender = case_when(
    female_percent == 1.0 ~ "female",
    female_percent == 0.0 ~ "male",
    TRUE ~ "mixed"
  ) %>% factor(levels = c("mixed", "female", "male")),

  # Mean sample age in months, centered around the mean
  age = age_mean / 30.417,
  age = age - mean(age, na.rm = TRUE),
  .keep = "unused"

) -> dat
```

```{r, meta_analysis}
# Three-level model
res_ml <- rma.mv(
  gi, vi,
  random = ~ 1 | article / experiment,
  data = dat,
  slab = experiment
)
print(res_ml)
# forest(res_ml)

# # Profile likelihodd plots for checking that REML has converged
# profile(res_ml)
```

```{r, meta_analysis_bayes}
# Specify priors
prior_c <- c(
  set_prior("normal(0, 1)", class = "Intercept"),
  set_prior("cauchy(0, 0.3)", class = "sd")
)

@@

## Moderator variables

```{r, meta_regression}
# Apply sliding difference contrast coding for the gender categories
# This means that the Intercept will be the grand mean (i.e., the average across
# studies) whereas the betas will test female vs. mixed and male vs. female
(contrasts(dat$gender) <- MASS::contr.sdif(3))

@@

# Supplementary information

```{r, prior_sens}
# Prior sensitivity analysis
list(
  "interept_uninformative" = c(
    set_prior("uniform(-3, 3)", class = "Intercept"),
    set_prior("cauchy(0, 0.3)", class = "sd")
  ),
  "interept_informative" = c(
    set_prior("normal(0, 0.2)", class = "Intercept"),
    set_prior("cauchy(0, 0.3)", class = "sd")
  ),
  "sd_uninformative" = c(
    set_prior("normal(0, 1)", class = "Intercept"),
    set_prior("uniform(0, 10)", class = "sd", ub = 10)
  ),
  "sd_informative" = c(
    set_prior("normal(0, 1)", class = "Intercept"),
    set_prior("student_t(10, 0, 0.2)", class = "sd")
  )
) %>%
  map(function(prior_sens) update(res_brm, prior = prior_sens)) -> res_sens
map(res_sens, summary)
```
